DAG test

### 2022-11-13 DAG.Rmd
old version

>>>>

```{r}
eq1= sfcr_set(

  part1 ~ beta_0 + beta_1*TSDEpart1,2 + beta_2*TSDELTALOG(TSLAG(part1,3))  +beta_3*TSDELTALOG(TSLAG(kont_h_ratio,1)) +beta_4*TSDELTALOG(rw_ds)  +beta_5*TSDELTALOG(TSLAG(rw_ds,2)) +beta_6*TSDELTALOG(TSLAG(rw_ds,3))  + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(kont_h_ratio,1)) + beta_11*TSLAG(ur_ds,1),

  ur_ds ~ rw_ds,

  rw_ds~ part1

)
```

```{r, fig.width=15, fig.height=7}
sfcr_dag_cycles_plot(eq1, size = 4)
```
